Achieving maximum possible precision on stellar radial-velocity measurements in multi-epoch spectroscopy

### 2017-11-29 paper/paper.tex
additive

additional noise considerations:
\begin{itemize}
\item (micro-) telluric features: tellurics that you can't identify are important
\item subtle continuum trends: not that big a deal
\item cosmic rays?: we might skip this.
\end{itemize}

@@

>>>>

additional noise considerations:
\begin{itemize}
\item (micro-) telluric features: tellurics that you can't identify are important
\item subtle continuum trends: not that big a deal
\item cosmic rays?: we might skip this and add to discussion
\item additive signals?: for example sky emission, lunar and other reflected solar; we might skip this and just add to discussion
\end{itemize}

@@

limitations of our ``additional noise'' ideas and what we have considered.

Hogg: insert some grand final statement.
